Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in Microservice-based applications
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}\textbf{}

>>>>

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in Microservice-based application
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}

Seeing the needs of the PRA system above, the approach the will be carried out to do performance regression analysis will be Cummulative Analysis and Aggregation Analysis.

Cummulative Analysis is an approach to analyze certain metrics of application such as latency by cummulating all the collected data as a single representation such as Histogram. With this approach, the distributed nature of many services in Microservice-based application can be observed as a single figure or representation so that the whole Microservice application can be monitored in a single space. One of the available tool to analyze and compare large sets of data is called Kolmogorov-Smirnov statistic test. Kolmogorov-Smirnov statistic test will count the difference between two Cummulative Distribution Functions (CDF) as a scalar number \cite{kolmogorov_1951}.
